\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-08 coqimpl.tex
edits

For the further-bindables, \lsti{Axiom}s declared in the module types must be instantiated.
%
\begin{itemize}[align=left,itemsep=5pt,labelsep=*,leftmargin=*]

\item
For \lsti{tm},
an inductive type \lsti{tm\_} is generated, with \lsti{tm\_}
instantiating the axiomatized \lsti{tm} type, and with
its constructors (\lsti{tm_unit\_} etc.) instantiating 
the axiomatized constructors (\lsti{tm_unit} etc.).
%
The partial recursor \lsti{tm_prect_STLC} is instantiated
%to \lsti{\lambda}\,\lsti{P, tm\__rect (\lambda}\,\lsti{t, option (P t))},
with the help of \lsti{tm\_rect}, the recursor of the generated \lsti{tm\_} type.
Proving the equalities on \lsti{tm_prect_STLC} is then trivial, by \lsti{reflexivity}.

\item
Similarly, \lsti{subst} is instantiated by applying the recursor \lsti{tm\_rect}
to the (already included) case handlers (\lsti{subst\_tm_unit}, etc.).
Propositional equalities on \lsti{subst} are then trivial, by \lsti{reflexivity}.

@@

Module \lsti{STLCFix} in \cref{fig:stlcfix-compiled} is generated upon
\lsti{End}~\lsti{STLCFix}, in the same fashion described above for \lsti{STLC}.
The translation makes code and proof sharing evident.
For example, the four case handlers for \lsti{subst} compiled for \lsti{STLC}
are reused by module \lsti{STLCFix}. So is the proof of \lsti{typesafe}.

>>>>

For the further-bindables, \lsti{Axiom}s declared in the module types must be instantiated.
%
\begin{itemize}[align=left,itemsep=0pt,labelsep=*,leftmargin=*]

\item
An inductive type \lsti{tm} is generated, instantiating the axiomatized
\lsti{tm} type and its constructors.
%
The partial recursor \lsti{tm_prect_STLC} is defined
%to \lsti{\lambda}\,\lsti{P, tm_rect (\lambda}\,\lsti{t, option (P t))},
with the help of \lsti{tm_rect}, the recursor Coq generates for \lsti{tm}.
Proving the equalities on \lsti{tm_prect_STLC} is then trivial, by \lsti{reflexivity}.

\item
Similarly, \lsti{subst} is instantiated by applying the recursor \lsti{tm_rect}
to the (already included) case handlers (\lsti{subst\_tm_unit}, etc.).
Propositional equalities on \lsti{subst} are then trivial, by \lsti{reflexivity}.

@@

Module \lsti{STLCFix} in \cref{fig:stlcfix-compiled} is generated upon
\lsti{End}~\lsti{STLCFix}, in the same fashion described above for \lsti{STLC}.
The translation makes code and proof sharing evident.
For example, the four case handlers (\lsti{subst\_tm_var} etc.) compiled for \lsti{STLC}
are reused to instantiate \lsti{subst}.
Translations of the definition of \lsti{env} and the proof of \lsti{typesafe},
are also reused to construct module \lsti{STLCFix}.

### 2022-11-08 stlc-compiled.tex
edits

Axiom subst_tm_abs_eq : [@\dadada@].
Axiom subst_tm_app_eq : [@\dadada@].

@@

Inductive tm\_ : Set :=[@\tanc{c-STLC-d-tm-start}@]
| tm_unit\_[@\,@]:[@\,@]tm\_ | tm_var\_[@\,@]:[@\,@]id -> tm\_
| tm_abs\_[@\,@]:[@\,@]id->tm\_->tm\_ | tm_app\_[@\,@]:[@\,@]tm\_->tm\_->tm\_.
[@\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm := tm\_.
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.

@@

Def tm_prect_STLC := \lambda P, tm\__rect (\lambda[@\,@]t, option (P t)).
Fact[@\;@][@\textls[-20]{tm\_unit\_eq\_STLC}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-tm-end}@][@\innersep@]

@@

Def subst[@\,@] := tm\__rect _ subst\_tm_unit subst\_tm_var
                        subst\_tm_abs  subst\_tm_app.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLC-d-subst-end}@][@\tanc{c-STLC-firstcol-end}@][@\innersep@]

>>>>

Axiom [@\dadada@]

@@

[@\codecomment{Instantiate \texttt{tm} \& its constructors}@][@\tanc{c-STLC-d-tm-start}@]
Inductive tm : Set :=
| tm_unit : tm | tm_var : id -> tm
| tm_abs : id -> tm -> tm | tm_app : tm -> tm -> tm.

@@

Def tm_prect_STLC := \lambda P, tm_rect (\lambda[@\,@]t, option (P t)).
Fact [@\textls[-20]{tm\_unit\_eq\_STLC}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.
Fact [@\dadada@][@\tanc{c-STLC-d-tm-end}@][@\innersep@]

@@

Def subst[@\,@] := tm_rect _ subst\_tm_unit
  subst\_tm_var subst\_tm_abs subst\_tm_app.
Fact [@\textls[-40]{subst\_tm\_unit\_eq}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.
Fact [@\dadada@][@\tanc{c-STLC-d-subst-end}@][@\tanc{c-STLC-firstcol-end}@][@\innersep@]

### 2022-11-08 stlcfix-compiled.tex
edits

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Cases\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases
[@\outdent@](self : STLCFix\_subst\_Cases\_Ctx).
Include STLC\_subst\_Cases(self).
Def subst\_tm_fix := [@\dadada@].
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_subst\_Cases.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@][@\textls[-30]{STLCFix}@]\_[@\textls[-30]{subst}@]\_[@\textls[-30]{Ctx}@]).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted for other fields defined in \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon conclusion of \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
Inductive tm\_ : Set :=[@\tanc{c-STLCFix-d-tm-start}@]
| tm_unit\_[@\,@]:[@\,@]tm\_ | tm_var\_[@\,@]:[@\,@]id -> tm\_
| tm_abs\_[@\,@]:[@\,@]id->tm\_->tm\_ | tm_app\_[@\,@]:[@\,@]tm\_->tm\_->tm\_
| tm_fix\_[@\,@]:[@\,@]id->tm\_->tm\_.
[@\codecomment{Instantiate \texttt{tm} \& its constructors}@]
Def tm := tm\_.
Def tm_unit := tm_unit\_. Def tm_var := tm_var\_.
Def tm_abs  := tm_abs\_.  Def tm_app := tm_app\_.
Def tm_fix  := tm_fix\_.
[@\codecomment{Instantiate \texttt{tm} partial recursors \& their equalities}@] [@\dadada@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\codecomment{Instantiate \texttt{subst} \& its equalities}@]
Def subst := tm\__rect _ subst\_tm_unit subst\_tm_var
             subst\_tm_abs  subst\_tm_app subst\_tm_fix.
Fact[@\;@][@\textls[-40]{subst\_tm\_unit\_eq}@][@\,@]:[@\,@][@\dadada@].[@\,@][@\textls[-40]{{\color{dkblue}reflexivity}.}@][@\,@]Qed.[@\hfill@]Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\codecomment{\textls[-10]{Instantiate \texttt{ty}, its constructors, partial recursor \& eq.}}@] [@\dadada@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{Include \texttt{env}}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\codecomment{Include/Instantiate other fields of \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

\makeline[-1pt]{c-STLCFix-tm-start}{c-STLCFix-tm-end}[codecomment-color!50][1.8pt]
\makeline[-1pt]{c-STLCFix-subst-start}{c-STLCFix-subst-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-rest}{c-STLCFix-rest}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-start}{c-STLCFix-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-tm-start}{c-STLCFix-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-subst-start}{c-STLCFix-d-subst-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-ty}{c-STLCFix-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-env}{c-STLCFix-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-rest}{c-STLCFix-d-rest}[codecomment-color!35][1.0pt]

>>>>

\begin{lstlisting}
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{tm} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-tm-start}@]
[@\outdent@]Module Type STLCFix\_tm\_Ctx.
[@\outdent@]End STLCFix\_tm\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_tm (self : STLCFix\_tm\_Ctx).
Include STLC\_tm(self).
Axiom tm_fix : id -> tm -> tm.
Axiom tm_fix_eq_STLC : \forall[@\,@][@\dadada@],[@\,@]tm_prect_STLC [@\dadada@][@\;@]=[@\;@]None.
Axiom tm_prect_STLCFix : [@\dadada@].
Axiom tm_fix_eq_STLCFix : [@\dadada@].
[@\outdent@]End STLCFix\_tm.[@\tanc{c-STLCFix-tm-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted upon definition of \texttt{subst} in \texttt{STLCFix}}@][@\tanc{c-STLCFix-subst-start}@]
[@\outdent@]Module Type STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_tm\_Ctx. Include STLCFix\_tm.
[@\outdent@]End STLCFix\_subst\_Cases\_Ctx.[@\innersep@]
[@\outdent@]Module STLCFix\_subst\_Cases
[@\outdent@](self : STLCFix\_subst\_Cases\_Ctx).
Include STLC\_subst\_Cases(self).[@\hfill\codecomment{reuse}@]
Def subst\_tm_fix := [@\dadada@].[@\hfill\codecomment{translation of new case}@]
[@\outdent@]End STLCFix\_subst\_Cases.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst\_Ctx.
Include STLCFix\_subst\_Cases\_Ctx.
Include STLCFix\_subst\_Cases.
[@\outdent@]End STLCFix\_subst\_Ctx.[@\innersep@]
[@\outdent@]Module Type STLCFix\_subst (self[@\,@]:[@\,@][@\textls[-30]{STLCFix}@]\_[@\textls[-30]{subst}@]\_[@\textls[-30]{Ctx}@]).
Include STLC\_subst(self).
Axiom subst_tm_fix_eq : [@\dadada@].
[@\outdent@]End STLCFix\_subst.[@\tanc{c-STLCFix-subst-end}@][@\outersep@]
[@\outdent@][@\codecomment{Code emitted for other fields defined in \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-rest}@][@\outersep@]
[@\outdent\codecomment{Code emitted upon conclusion of \texttt{STLCFix}}@][@\tanc{c-STLCFix-start}@]
[@\outdent@]Module STLCFix.[@\innersep@]
[@\codecomment{Instantiate \texttt{tm} \& its constructors}@][@\tanc{c-STLCFix-d-tm-start}@]
Inductive tm : Set :=
| tm_unit : tm | tm_var : id -> tm
| tm_abs : id -> tm -> tm | tm_app : tm -> tm -> tm
| tm_fix : id -> tm -> tm.
[@\codecomment{Instantiate \texttt{tm} partial recursors \& their equalities}@] [@\dadada@][@\tanc{c-STLCFix-d-tm-end}@][@\innersep@]
Include STLCFix\_subst\_Cases. [@\tanc{c-STLCFix-d-subst-start}@]
[@\codecomment{Instantiate \texttt{subst} \& its equalities}@]
Def subst := tm_rect _ subst\_tm_unit
subst\_tm_var subst\_tm_abs subst\_tm_app[@\hfill\codecomment{reuse}@]
subst\_tm_fix.
Fact [@\textls[-40]{subst\_tm\_unit\_eq}@] : [@\dadada@]. [@\textls[-40]{{\color{dkblue}reflexivity}.}@] Qed.
Fact [@\dadada@][@\tanc{c-STLCFix-d-subst-end}@][@\innersep@]
[@\codecomment{\textls[-10]{Include\;\texttt{ty}, its constructors, partial recursor \& eq.}}@] [@\dadada@][@\tanc{c-STLCFix-d-ty}@][@\innersep@]
Include STLC\_env.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-env}@][@\innersep@]
[@\codecomment{Include/Instantiate other fields of \texttt{STLCFix}}@] [@\dadada@][@\tanc{c-STLCFix-d-rest}@][@\innersep@]
Include STLC\_typesafe.[@\hfill\codecomment{reuse}@][@\tanc{c-STLCFix-d-typesafe}@][@\innersep@]
[@\outdent@]End STLCFix.[@\tanc{c-STLCFix-end}@]
\end{lstlisting}

\makeline[-1pt]{c-STLCFix-tm-start}{c-STLCFix-tm-end}[codecomment-color!50][1.8pt]
\makeline[-1pt]{c-STLCFix-subst-start}{c-STLCFix-subst-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-rest}{c-STLCFix-rest}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+8pt]{c-STLCFix-start}{c-STLCFix-end}[codecomment-color!50][1.8pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-tm-start}{c-STLCFix-d-tm-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-subst-start}{c-STLCFix-d-subst-end}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-ty}{c-STLCFix-d-ty}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-env}{c-STLCFix-d-env}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-rest}{c-STLCFix-d-rest}[codecomment-color!35][1.0pt]
\makeline[.5\textwidth+12pt]{c-STLCFix-d-typesafe}{c-STLCFix-d-typesafe}[codecomment-color!35][1.0pt]
